Age-related changes in plant growth and traits

### 2015-09-01 Growth_figs.rmd
Tidy up use of remake and functions
Continued little fixes to main files (Growth_figs, RA_figs) - they now run in Knitr again
Some additional work in RA_figs, incorporating what we talked about in lab meeting last Thursday

```{r, echo=FALSE,results='hide', message=FALSE,warning=FALSE}
library(remake)
create_bindings()

source("scripts/functions.R")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.mature(data[[spp]]$mature)
}

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_leaf"
xvar <- "total_weight"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
                    main=spp,col=col.age(data[[spp]]$age)
}

mtext("Investment in leaves (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_stem"
xvar <- "total_weight"

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
                    main=spp,col=col.age(data[[spp]]$age)
}

mtext("Investment in stems (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age)
  abline(0,1)
}

mtext("increase in stem diameter (mm)", 2, outer=TRUE,cex=1.2)
mtext("increase in shoot diameter (mm)", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=0.9,bty="n")
```

####Plots of increase in whole plant versus shoot leaf area  
* Very different, patterns across species

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age)
  abline(0,1)
}

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
plot(LL_death~shoot_leaf_area,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp(species))
mod <- lm(log(shoot_leaf_area)~LL_death,data=subset(SummaryInd,LL_death<6))
words.top.right.logx(mod)

plot(LL_death~leaf_area,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp(species))
mod <- lm(log(leaf_area)~LL_death,data=subset(SummaryInd,LL_death<6))
words.top.right.logx(mod)
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age)
}

mtext("ll death", 2, outer=TRUE,cex=1.2)
mtext("shoot leaf area", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
```

***leaf lifespan vs. whole plant leaf area***  
*the regression results below exclude young individuals  
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "LL_death"
xvar <- "leaf_area"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age)
}

mtext("ll death", 2, outer=TRUE,cex=1.2)
mtext("leaf area", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")

yvar <- "LL_death"
xvar <- "leaf_area"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age)
}

mtext("growth_stem_diameter", 2, outer=TRUE,cex=1.2)
mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_leaf_area"
xvar <- "prop_maxH"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age)
}

mtext("increase in leaf area", 2, outer=TRUE,cex=1.2)
mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "total_weight"
xvar <- "prop_maxH"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age)
}

mtext("total size", 2, outer=TRUE,cex=1.2)
mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "total_weight"
xvar <- "prop_maxH"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.mature(data[[spp]]$mature)
}

mtext("total size", 2, outer=TRUE,cex=1.2)
mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
```

@@

plot(wood_density~growth_leaf_area,SummaryInd,log="y",pch=16,col=col.age(age)
mod <- lm(log(growth_leaf_area)~age*wood_density,SummaryInd)
summary(mod)
```

>>>>

```{r,message=FALSE,warning=FALSE, echo=FALSE}
remake::make("export")

SummaryInd <- readRDS("export/SummaryInd.rds")
SummarySpp <- readRDS("export/SummarySpp.rds")
SummarySppAge <- readRDS("export/SummarySppAge.rds")

source("R/figures.R")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.mature(data[[spp]]$mature))
}

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_leaf"
xvar <- "total_weight_0"

data <- subset(SummaryInd,growth_leaf>0)
data <- split(data, data$species)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
                    main=spp,col=col.age(data[[spp]]$age))
}

mtext("Investment in leaves (mg)", 2, outer=TRUE,cex=1.2)
mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_stem"
xvar <- "total_weight_0"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
                    main=spp,col=col.age(data[[spp]]$age))
}

mtext("Investment in stems (mg)", 2, outer=TRUE,cex=1.2)
mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age))
}

mtext("increase in stem diameter (mm)", 2, outer=TRUE,cex=1.2)
mtext("increase in shoot diameter (mm)", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=0.9,bty="n")
```

####Plots of increase in whole plant versus shoot leaf area  
* Very different, patterns across species
* Overall, the earlier successional species show a stronger correlation (BOLE, COER, HEPU, PHPH, GRSP) suggesting what is happening at the shoot level matters more to these species

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age))
}

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
plot(LL_death~shoot_leaf_area_0,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp(species))
mod <- lm(log(shoot_leaf_area_0)~LL_death,data=subset(SummaryInd,LL_death<6&shoot_leaf_area_0>0))
words.top.right.logx(mod)

plot(LL_death~leaf_area_0,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp(species))
mod <- lm(log(leaf_area_0)~LL_death,data=subset(SummaryInd,LL_death<6))
words.top.right.logx(mod)
```

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age))
}

mtext("ll death", 2, outer=TRUE,cex=1.2)
mtext("shoot leaf area", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

***leaf lifespan vs. whole plant leaf area***  
*the regression results below exclude young individuals  
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "LL_death"
xvar <- "leaf_area_0"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age))
}

mtext("ll death", 2, outer=TRUE,cex=1.2)
mtext("initial leaf area", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")

yvar <- "LL_death"
xvar <- "leaf_area_0"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age))
}

mtext("growth_stem_diameter", 2, outer=TRUE,cex=1.2)
mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_leaf_area_log"
xvar <- "prop_maxH"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age))
}

mtext("increase in leaf area (log(LA_final)-log(LA_initial))", 2, outer=TRUE,cex=1.2)
mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "total_weight_0"
xvar <- "prop_maxH"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.age(data[[spp]]$age))
}

mtext("initial size", 2, outer=TRUE,cex=1.2)
mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

###RSOM: species differ in how much they increase in height after the onset of reproduction.   
  * Late reproducing, taller species increase less in height after the onset of reproduction

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "total_weight_0"
xvar <- "prop_maxH"

@@

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                    main=spp,col=col.mature(data[[spp]]$mature))
}

mtext("intial size", 2, outer=TRUE,cex=1.2)
mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
legend("bottomright",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
```

@@

plot(wood_density~growth_leaf_area,SummaryInd,log="y",pch=16,col=col.age())
mod <- lm(log(growth_leaf_area)~age*wood_density,SummaryInd)
summary(mod)
```
